% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,headheight=3ex,headsep=3ex]{geometry}
\usepackage{graphicx}
\usepackage{float}

\newcommand{\blankline}{\quad\pagebreak[2]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify Course title, instructor name, semester here %%%%%%%%

\title{Syllabus of Math 33A: Linear Algebra and Applications}
\author{Stephanie Wang}
\date{Spring, 2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[sc]{mathpazo}
\linespread{1.05} % Palatino needs more leading (space between lines)
\usepackage[T1]{fontenc}
\usepackage[mmddyyyy]{datetime}% http://ctan.org/pkg/datetime
\usepackage{advdate}% http://ctan.org/pkg/advdate
\newdateformat{syldate}{\twodigit{\THEMONTH}/\twodigit{\THEDAY}}
\newsavebox{\MONDAY}\savebox{\MONDAY}{Mon}% Mon
\newcommand{\week}[1]{%
%  \cleardate{mydate}% Clear date
% \newdate{mydate}{\the\day}{\the\month}{\the\year}% Store date
  \paragraph*{\kern-2ex\quad #1, \syldate{\today} - \AdvanceDate[4]\syldate{\today}:}% Set heading  \quad #1
%  \setbox1=\hbox{\shortdayofweekname{\getdateday{mydate}}{\getdatemonth{mydate}}{\getdateyear{mydate}}}%
  \ifdim\wd1=\wd\MONDAY
    \AdvanceDate[7]
  \else
    \AdvanceDate[7]
  \fi%
}
\usepackage{setspace}
\usepackage{multicol}
%\usepackage{indentfirst}
\usepackage{fancyhdr,lastpage}
\usepackage{url}
\pagestyle{fancy}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{layout}

\lhead{}
\chead{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify header here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\rhead{\footnotesize Syllabus of Math 33A: Linear Algebra and Applications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\usepackage{array, xcolor}
\usepackage{color,hyperref}
\definecolor{clemsonorange}{HTML}{EA6A20}
\hypersetup{colorlinks,breaklinks,linkcolor=clemsonorange,urlcolor=clemsonorange,anchorcolor=clemsonorange,citecolor=black}

\begin{document}

\maketitle

\begin{tabular*}{.93\textwidth}{@{\extracolsep{\fill}}lr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hline
 & \\
 Class Hours: MWF 2-2:50pm & Class Room: Math Sciences 5147 \\
 Office Hours: MWF 1-1:50pm  &  Office: Math Sciences 7601 \\
 E-mail: \texttt{evast@g.ucla.edu} & CCLE: \href{https://ccle.ucla.edu/course/view/19S-MATH33A-4}{ccle.ucla.edu/course/view/19S-MATH33A-4}\\ 
 & \\
\hline
\end{tabular*}

\vspace{5 mm}

% First Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{General Informations}
\begin{itemize}
  \item {\bf Textbook:} O. Bretscher, Linear Algebra, 5th Ed., Prentice Hall.
  \item {\bf Course Outline:} Detailed course description and tentative lecture schedule at \\ \href{https://www.math.ucla.edu/ugrad/courses/math/33A}{https://www.math.ucla.edu/ugrad/courses/math/33A}. This course covers Chapter 1-3 and 5-8 of the textbook.
  \item {\bf Exams:} Two in-class midterm exams (50 minutes) on \textbf{\textit{April 22nd}} the Monday and \textbf{\textit{May 13th}} the Monday. Cumulative/comprehensive final exam (180 minutes) on \textbf{\textit{June 13th}} the Thursday. No make-up exam: you have to attend final to pass, and you can drop one midterm.
  \item {\bf Homework/Quizzes:} Weekly homework assigned each Monday on \href{https://ccle.ucla.edu/course/view/19S-MATH33A-4}{CCLE} and due on Friday. First 10 minutes of Friday lecture are dedicated to in-class quizzes. Homework and quiz should be submitted and will be graded together. Homework is graded based on completion. 

\end{itemize}

\section*{Grading Policy}
Two lowest homework/quiz grades are dropped to accommodate medical reasons and technical difficulties, etc. Course grades are given based on the higher of the following two schemes:
\begin{itemize}
  \item 15\% Homework/Quizzes + 20\% Midterm 1 + 20\% Midterm 2 + 45\% Final
  \item 10\% Homework/Quizzes + 35\% (Best of two Midterms) + 55\% Final
\end{itemize}
Shall any curving take place, the curving will preserve percentile and your curved grade is guaranteed larger than or equal to your original one.
\end{document}
